Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-03-05 paper.tex
agregue la palabra set en la linea 412
borre comentarios que no voy a usar en el tex

\usepackage{verbatim} % comentarios
\usepackage{epsfig}
\usepackage{amssymb}

\usepackage{mathtools}

\usepackage{lineno}

\usepackage{tikz}        %permite rellenar las figuras (circulos)
\usepackage{etoolbox}
%\usepackage[backend=biber,citestyle=authoryear]{biblatex}
\usepackage{ulem}         %permite el tachado de texto.

%\usepackage{epstopdf}

\usepackage[caption=false]{subfig}

@@

The numerical of the parameters may affect the dynamics of the  pedestrians.
Some values, however, yield similar collective dynamics. We introduce
dimensionless magnitudes  and proceed straightforward as indicated in
\ref{appendix1}. We realize from  \ref{appendix1} that only three
(dimensionless) parameters  are the true  ``control'' parameters for the
collective dynamics. These are $\mathcal{A}$,  $\mathcal{K}$, $\mathcal{K}_c$ as
defined in \ref{appendix1}. Recall that  $\mathcal{A}$ and $\mathcal{K}$ are
precisely the same as in  Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$
parameter has been  introduced due to the body force.   \\

@@

%It is worth mentioning that the SFM contemplates the possibility of overlapping
%between pedestrians (unlike the models stated in
%Refs.~\cite{kabalan_2017,jebrane_2019}). Despite this hard-to-interpret
%feature, the SFM can reproduce empirical behaviors of collective pedestrian
%dynamics.\\

@@

\begin{comment}
Fig. \ref{flow_density} shows the flow as a function of the global density 
(fundamental diagram). \ref{flow_density_no_body_force} corresponds to zero body
 force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds 
 to a body force with $k_n=1.2\,$E5. Each curve correspond to a different 
 friction value (see the caption).\\

According to most of the empirical measurements, the flow decreases for high 
enough values of density because the crowd becomes jammed. Notice that the 
original friction does not produce a reduction of the flow when there is zero 
body force but when the body force is included (with the original SFM value), 
the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher 
values of density. When the friction is five times the original value, the flow 
reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force 
and without body force). The main qualitative difference is that including the 
body force produces a subtle increment in the flow for densities higher than 
7 p m$^{-2}$. When the friction is increased by a factor of ten, the flow 
reduces or remains constant when the density is higher than 5 p m$^{-2}$ for 
both cases (with body force and without body force). This result suggests that 
even including the body force, the original SFM requires an increment of the 
friction in order to reproduce the flow reduction reported in empirical 
measurements.\\
\end{comment}

>>>>

\usepackage{verbatim} % comentarios
\usepackage{epsfig}
\usepackage{amssymb} 
\usepackage{mathtools}
\usepackage{lineno}
\usepackage{tikz}        %permite rellenar las figuras (circulos)
\usepackage{etoolbox}
\usepackage{ulem}         %permite el tachado de texto.
\usepackage[caption=false]{subfig}

@@

The numerical set of parameters may affect the dynamics of the  pedestrians.
Some values, however, yield similar collective dynamics. We introduce
dimensionless magnitudes  and proceed straightforward as indicated in
\ref{appendix1}. We realize from  \ref{appendix1} that only three
(dimensionless) parameters  are the true  ``control'' parameters for the
collective dynamics. These are $\mathcal{A}$,  $\mathcal{K}$, $\mathcal{K}_c$ as
defined in \ref{appendix1}. Recall that  $\mathcal{A}$ and $\mathcal{K}$ are
precisely the same as in  Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$
parameter has been  introduced due to the body force.   \\

@@

@@
